%! TEX root = ../cv.tex

\section{\sc Open Source Contributions}

{\bf \href{https://github.com/pulls?q=author%3Aznculee+is%3Amerged}{Merged Pull Requests}}
\begin{itemize}
    \item \href{https://github.com/giorginolab/zotfile_doctor}{giorginolab/zotfile\_doctor} \\
        A tool checking consistency between Zotfile's file storage and the corresponding Zotero's view.
        \begin{itemize}
            \item \href{https://github.com/giorginolab/zotfile_doctor/pull/5}{Add cleaning feature for this tool.}
        \end{itemize}
    \item \href{https://github.com/facebookresearch/TreeNLG}{facebookresearch/TreeNLG} \\
        A novel method of constrained decoding for neural NLG (NNLG) models.
        \begin{itemize}
            \item \href{https://github.com/facebookresearch/TreeNLG/pull/5}{Make the code work with public fairseq, fix bugs and add new features.}
        \end{itemize}
    \item \href{https://github.com/lervag/vimtex}{lervag/vimtex} \\
        A modern vim plugin for editing \LaTeX~files.
        \begin{itemize}
            \item \href{https://github.com/lervag/vimtex/pull/1178}{Refine the experience in forward search with Skim.}
        \end{itemize}
    \item \href{https://github.com/THUNLP-MT/THUMT}{THUNLP-MT/THUMT} \\
        An open-source neural machine translation toolkit developed by Tsinghua Natural Language Processing Group.
        \begin{itemize}
            \item \href{https://github.com/THUNLP-MT/THUMT/pull/45}{Add de-BPE during evaluation.}
        \end{itemize}
\end{itemize}

{\bf \href{https://github.com/znculee?tab=repositories}{Created Repositories}}
\begin{itemize}
    \item \href{https://github.com/znculee/align-label-tool}{znculee/align-label-tool} \\
        A commend line tool for labeling alignments of parallel sentences.
    \item \href{https://github.com/znculee/fish-theme-xtli}{znculee/fish-theme-xtli} \\
        An elegant auto-adapt prompt to fish shell.
\end{itemize}
